Geometrization of characters of tori over non-Archimedean local fields

### 2013-08-12 shanghai.tex
Finished the first lemma on finite geochars.
Working on the second lemma on geochars this evening  . . .

\begin{proof}
The main issue to address is well-definedness. Although the pull-back appearing in the diagram above it not unique, the recipe for $g^*$ is well-defined as a functor between localized categories.
To see this, recall that a morphism in $\GCf(G)$ is an equivalence class of a diagram like \eqref{eq:morGCf}, commonly denoted by $(\alpha_1,T_1)^{-1}\circ (\alpha'_1,T'_1)$. 
The equivalence relation identifies $(\alpha_1,T_1)^{-1}\circ (\alpha'_1,T'_1)$
 with $(\alpha_2,T_2)^{-1}\circ (\alpha'_2,T'_2)$ if there are maps 
 $(f_1,\psi_1)\to (f_0,\psi_0)$ and $(f_2,\psi_2)\to (f_0,\psi_0)$ making the following diagram commute
 \[
  \begin{tikzcd}
  \  & A & \\
B   & C & D \\
  & E &
  \end{tikzcd}
 \]
 where $(f',\psi') \to (f_0,\psi_0)$ is a weak isomorphism.

\end{proof}

>>>>

\begin{proof}
The key point is that pull-back along $g$ takes isogenies to isogenies, and maps over $G$ to maps over $G'$, as pictured below.
\[
\begin{tikzcd}[row sep=10,column sep=10]
\ & V \arrow{dd}{T} && \Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} && H \arrow{rr}{f} && \arrow[equal]{dd} G\\
 && && \arrow{ul} \ker f\times_G G' \arrow{ur} \arrow[hook]{rr} && H\times_G G' \arrow{ur} \arrow{rr} && G' \arrow{ur}{g} & \\
& V' && \Aut(V) && \arrow[swap]{ll}{\psi'} \arrow[swap]{uu}{} \ker f'  \arrow[hook]{rr} && \arrow[swap]{uu} H' \arrow{rr}{f'} && G\\
 && && \arrow{ul} \ker f'\times_G G' \arrow{uu} \arrow{ur} \arrow[hook]{rr} && \arrow{uu} H'\times_G G' \arrow{ur} \arrow{rr} && \arrow[equals]{uu} G' \arrow{ur}{g} & \\
\end{tikzcd}
\]
In this form we could treat $g^*$ as a functor $G(G')\to C(G)$, where it not for the fact that pull-back is defined only up to isomorphism. In the localized categories, this ambiguity disappears. 
\end{proof}
